An Empirical Analysis of the Benefits of Adaptive Gradient Methods

### 2017-12-04 Project/Presentation/main.tex
Added Optimizers slides

\begin{frame}{Outline}
\tableofcontents
\end{frame}

@@

\section{Adaptive Gradient Methods}
\begin{frame}{Introduction to Adaptive Gradient Methods}
\uncover<1->{General form of any adaptive gradient method is: \[\xbold_{t+1} := \xbold - \eta_{t}\g_{\xbold_{t}} f(\xbold_{t})\] where \(\xbold_{t}\) is the value of \(\xbold\) at iteration \(t\)}
\(\newline\)

@@

>>>>

@@

\section{Adaptive Gradient Methods}
\subsection{Introduction}
\begin{frame}{Introduction to Adaptive Gradient Methods}
\uncover<1->{General form of any adaptive gradient method is: \[\xbold_{t+1} := \xbold - \eta_{t}\g_{\xbold_{t}} f(\xbold_{t})\] where \(\xbold_{t}\) is the value of \(\xbold\) at iteration \(t\)}
\(\newline\)

@@

\subsection{Adagrad}
\begin{frame}{Adagrad} % add citations
\uncover<1->{Define: \[G_{t} \triangleq \mathrm{diag}\left(\displaystyle \sum_{i=0}^{t} \g f(\xbold_{i}) \odot \g f(\xbold_{i})\right)\]}
\uncover<2->{Adagrad updates parameters based on the rule below:
\begin{equation}
\label{adagrad}
\xbold_{t+1} = \xbold_{t} - \frac{\eta}{\sqrt{G_{t} + \epsilon}} \odot \g f(\xbold_{t})
\end{equation}
where \(\epsilon\) is a small value to prevent divide by zero errors
}
\end{frame}

\subsection{Adadelta}
\begin{frame}{Adadelta} % add citations
\uncover<1->{Define: \[g_{t} \triangleq \g f(\xbold_{t}) \odot \g f(\xbold_{t})\]
\[\mathbb{E}[g]_{t} \triangleq \rho\mathbb{E}[g]_{t-1} + (1 - \rho)g_{t}\]
\[\Delta \xbold_{t} \triangleq -\eta\displaystyle\frac{\sqrt{\mathbb{E}[\Delta \xbold]_{t-1} + \epsilon}}{\sqrt{\mathbb{E}[g]_{t} + \epsilon}}\odot\g f(\xbold_{t})\]
\[\mathbb{E}[\Delta \xbold]_{t} \triangleq \rho\mathbb{E}[\Delta \xbold]_{t-1} + (1 - \rho)\left(\Delta \xbold_{t} \odot \Delta \xbold_{t}\right)\]}
\uncover<2->{Adadelta updates parameters based on the rule below:
\begin{equation}
\label{adadelta}
\xbold_{t+1} = \xbold_{t} + \Delta \xbold_{t}
\end{equation}
where \(\epsilon\) is a small value to ensure stability/relieve divide by zero errors.
}
\end{frame}

\subsection{Adam}
\begin{frame}{Adam} % add citations
\uncover<1->{Define: \[m_{t} \triangleq \beta_{1}m_{t-1} + (1 - \beta_{1})\g f(\xbold_{t}), \hspace{3mm} v_{t} \triangleq \beta_{2}v_{t-1} + (1 - \beta_{2})\left(\g (\xbold_{t}) \odot \g (\xbold_{t})\right)\]
\[\hat{m}_{t} \triangleq \displaystyle \frac{m_{t}}{1 - \beta_{1}^{t}}, \hspace{3mm} \hat{v}_{t} \triangleq \displaystyle \frac{v_{t}}{1 - \beta_{2}^{t}}\]
}
\uncover<2->{Adam updates parameters based on the rule below:
\begin{equation}
\label{adam}
\xbold_{t+1} = \xbold_{t} - \frac{\eta}{\sqrt{\hat{v}_{t}} + \epsilon} \odot \hat{m}_{t}
\end{equation}
where \(\epsilon\) is a small value to prevent divide by zero errors
}
\end{frame}

\subsection{RMSProp}
\begin{frame}{RMSProp} % add citations
\uncover<1->{Define: \[g_{t} \triangleq \g f(\xbold_{t}) \odot \g f(\xbold_{t})\]
\[\mathbb{E}[g]_{t} \triangleq 0.9\mathbb{E}[g]_{t-1} + 0.1g_{t}\]
}
\uncover<2->{RMSProp updates parameters based on the rule below:
\begin{equation}
\label{rmsprop}
\xbold_{t+1} = \xbold_{t} - \frac{\eta}{\sqrt{\mathbb{E}[g]_{t} + \epsilon}} \odot \g f(\xbold_{t})
\end{equation}
where \(\epsilon\) is a small value to prevent divide by zero errors
}
\end{frame}
